\documentclass[nobib]{tufte-handout}

\title{Graph Representation Learning\\
       \Large Notes\thanks{Authors: Eeshaan Jain \\ Notes of the book Graph Representation Learning by William L. Hamilton}}

\date{Winter 2021} % without \date command, current date is supplied

%\geometry{showframe} % display margins for debugging page layout

\usepackage{graphicx} % allow embedded images
  \setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
  \graphicspath{{notes1/fig/}} % set of paths to search for images
\usepackage{amsmath}  % extended mathematics
\usepackage{thmbox}
\usepackage{amstext}  % extended text
\usepackage{amsfonts}  % extended text
\usepackage{booktabs} % book-quality tables
\usepackage{units}    % non-stacked fractions and better unit spacing
\usepackage{multicol} % multiple column layout facilities
\usepackage{lipsum}   % filler text
\usepackage{fancyvrb} % extended verbatim environments
\usepackage{placeins}
\usepackage{sty/kbordermatrix}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tocloft}
\usepackage{listings}
\usepackage[many]{tcolorbox}
\tcbuselibrary{listings,skins}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}

\lstset{style=mystyle}

\renewcommand{\lstlistingname}{Algorithm}% Listing -> Algorithm
\renewcommand{\lstlistlistingname}{List of \lstlistingname s}% List of Listings -> List of Algorithms

\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

\hypersetup{
	colorlinks,
	citecolor=violet,
	linkcolor=red,
	urlcolor=blue}

  \fvset{fontsize=\normalsize}% default font size for fancy-verbatim environments

% Standardize command font styles and environments
\newcommand{\doccmd}[1]{\texttt{\textbackslash#1}}% command name -- adds backslash automatically
\newcommand{\docopt}[1]{\ensuremath{\langle}\textrm{\textit{#1}}\ensuremath{\rangle}}% optional command argument
\newcommand{\docarg}[1]{\textrm{\textit{#1}}}% (required) command argument
\newcommand{\docenv}[1]{\textsf{#1}}% environment name
\newcommand{\docpkg}[1]{\texttt{#1}}% package name
\newcommand{\doccls}[1]{\texttt{#1}}% document class name
\newcommand{\docclsopt}[1]{\texttt{#1}}% document class option name
\newenvironment{docspec}{\begin{quote}\noindent}{\end{quote}}% command specification environment
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\textunderscript}[1]{$_{\text{#1}}$}

\setcounter{secnumdepth}{3}
\newtheorem[M]{definition}{Definition}[section]

\begin{document}

\maketitle% this prints the handout title, author, and date

%\printclassoptions


\textbf{Keyphrases: Graph Representation Learning. Graph Statistics. Graph Kernel Methods. Graph Embeddings. Graph Neural Networks. Graph Generative Models.}

This set of notes begin by introducing graphs, and learning tasks on it. Then we discuss the traditional approaches to infer graphs at the node-level and graph-level and further see inter-node relations. This extends to Spectral Graph Theory and use of Graph Laplacians to perform optimal clustering. [Introduction will be updated as file is updated.]
\tableofcontents

\include{chapter1}
\include{chapter2}


\nocite{*}
\footnotesize
\bibliographystyle{apalike}
\bibliography{notes1/reference}

\end{document}
